---
title: "Baseball_Analysis"
author: "Bianca"
date: "2023-09-26"
output: pdf_document
---
Required Packages
```{r message=FALSE, warning=FALSE}
library(BiaDiss)
library(tidyverse)
library(xtable)
library(compositions) #Creates ternary diagrams
```


If we combine the three age groups into a single group, will the correlations be similar to what we saw when the data was parsed into age groups?  This code creates
table 7.1 on page 90 and table 7.4 on page 107.  I included the same table twice.

```{r}
temp <- BattersGrouped %>% select(HR:OTHER)
(group.cor <- round(cor(temp), 4))

#Creates latex code for table 7.4.
#xtable(group.cor, type=latex, digits = c(0, rep(4, 6)))
```

Next we break the data into 3 datasets by age group.

```{r}
age.1.data <- BattersGrouped %>% filter(GROUP==1) %>% select(HR:OTHER)
age.2.data <- BattersGrouped %>% filter(GROUP==2) %>% select(HR:OTHER)
age.3.data <- BattersGrouped %>% filter(GROUP==3) %>% select(HR:OTHER)
```

Check the correlation structure for each age group.  Are they similar
enough to grouped data correlation structure? Are there positive and negative correlations? This code creates Table 7.2 on page 106.

```{r}
(b1 <- round(cor(age.1.data), 4))
(b2 <- round(cor(age.2.data), 4))
(b3 <- round(cor(age.3.data), 4))

#Create the latex code for the table 7.2.
#xtable(b1, type=latex, digits = c(0, rep(4, 6)))
#xtable(b2, type=latex, digits = c(0, rep(4, 6)))
#xtable(b3, type=latex, digits = c(0, rep(4, 6)))
```

Create ternary diagrams for each age group seen on pages 92, 93, 94

I have commented these out because they were taking too long to run and they were unattractive.

```{r warning=FALSE}
batter.dat <- BattersGrouped %>% rename( "TRI" = TRIPLE,
                                     "DBL" = DOUBLE,
                                     "SGL" = SINGLE,
                                     "OTR" = OTHER)

age.1.data <- batter.dat %>% filter(GROUP==1) %>% select(HR:OTR)
age.2.data <- batter.dat %>% filter(GROUP==2) %>% select(HR:OTR)
age.3.data <- batter.dat %>% filter(GROUP==3) %>% select(HR:OTR)


##YY <- acomp(age.1.data + 0.00001)
##jpeg("fig_8_1_A.jpeg", width =800, height = 800, quality = 100)
##plot(YY, pch=20, cex=1,  main="Age Group 1 Ternary Diagrams")
##dev.off()


##YY <- acomp(age.2.data + 0.00001)
##jpeg("fig_8_1_B.jpeg", width =800, height = 800, quality = 100)
##plot(YY, pch=20, cex=1,  main="Age Group 2 Ternary Diagrams")
##dev.off()

##YY <- acomp(age.3.data + 0.00001)
##jpeg("fig_8_1_C.jpeg", width =800, height = 800, quality = 100)
##plot(YY, pch=20, cex=1,  main="Age Group 3 Ternary Diagrams")
##dev.off()

```

Returns the complete binary tree for the baseball dataset.  
```{r}
complete.bin.tree(BattersGrouped[,4:9])
```



